### 2021-05-16 chatbot_classification/03.emnlp_2021/methodology.tex
modified:   appendix.tex   modified:   experiments.tex   modified:   introduction.tex   modified:   methodology.tex

\section{Methodology}
In  this section, we describe our proposed SFC method, which includes the basic two-stage SFC and its more compact version joint SFC.

\subsection{Two-stage SFC}

@@

\begin{equation}
  \begin{aligned}
    \mathcal{L}^{C}&=\frac{1}{N}\sum_{i=1}^{N}-log(\frac{exp(\varPhi_{i,y_{i}}^C)}{\sum_{j=1}^{C}exp(\varPhi_{i,j}^C)}) \\
    \label{eq:classification_loss}
  \end{aligned}
\end{equation}

@@

\begin{table*}
  \begin{centering}
    \scalebox{0.75}{
      \begin{tabular}{|c|c|c|c|c|c|}
        \hline 
        \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} &
        \textbf{\#Training Samples} & \textbf{\#Samples/Class} & \textbf{Settings}\tabularnewline
        \hline 
        ITG & FAQ chatbot & 228 & 3938 * 0.7 & 12 & 3-fold\tabularnewline
        \hline 
        Amazon-670k & Product review & 250 & 2658 * 0.7 & 8 & 3-fold\tabularnewline
        \hline 
        HWU64 & intent detect & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
        CLINC150 & intent detect & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
        BANKING77 & intent detect & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
        FRAMES & intent detect with ner & 21 & [208, 408, 984] & [10, 20, 50] & data sampling\tabularnewline
        \hline
        ATIS & inent detect with ner & 21 & [168, 303, 544] & [10, 20, 50] & data sampling\tabularnewline
        \hline
      \end{tabular}
    }
    \par
  \end{centering}
  \caption{Statistics for all datasets and few shot settings.}

@@

\vspace{-1.25em}
\begin{equation}
  \begin{aligned}
    \mathcal{L}^{S}&=\frac{1}{M}\sum_{i=1}^{M}-w^S_{l_i}\cdot log(\frac{exp(\varPhi_{i,l_{i}}^S)}{\sum_{j=0}^{1}exp(\varPhi_{i,j}^S)}) \\
    \label{eq:similarity_loss}
  \end{aligned}
\end{equation}
\vspace{-1.75em}

@@

\begin{align}
  {\xi}_{i,j}^{K,pos} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,pos} \ \ \ \ \ \ \ 
  {\xi}_{i,j}^{K,neg} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,neg}
  \label{eq:average pooling}
\end{align}

@@

\begin{align}
  \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K
  \label{eq:two-stage_SFC_loss}
\end{align}

@@

    \scalebox{0.45}{

@@

        \multirow{2}*{Joint SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.9669}$} & \multirow{2}*{$\textbf{0.9712}$} & \multirow{2}*{$\textbf{0.9821}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.9323}$} & \multirow{2}*{$\textbf{0.9463}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$\textbf{0.7593}$} & \multirow{2}*{$\textbf{0.7772}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline

@@

\subsection{Joint SFC}
In  two-stage  SFC,  Stage  1  and  stage 2 are separate that there is no deep
interaction  with each other during training. In this case, the performance of
stage  1  may  limit  the potential of stage 2; meanwhile, stage 2 also cannot
give  training feedback back to stage 1 for fine-tuning. Therefore, to further
improve  the  overall performance of SFC, we proposed a joint model structure,
shown in Fig. \ref{fig:framework}.

In  joint  SFC,  classification  model is being placed in lower layer level to
dynamically  provide  top-K  candidate  class  labels  for  the  sentence-pair
similarity  model  placed in higher layer level through a top-K pooling layer.
In  this way, classification model and similarity model can be merged into one
single  joint-model  for  multi-task training with sentence pairs sampled from
varying  candidate  class  labels,  thus  avoiding the limitation brought by 2
separate stage structure.

There  are 3 tasks in total during the training process of joint SFC, shown in
Fig. \ref{fig:framework}, and the overall loss is also the weighted sum of all
the   task-specific  losses,  shown  in  Equ.  \ref{eq:joint_SFC_loss}.  Here,
$\alpha_S$,  $\alpha_K$  and  $\alpha_C$  represent  the  weights  for  task 1
sentence-pair  similarity  in  Equ.  \ref{eq:similarity_loss},  task  2  top-K
classification  in Equ. \ref{eq:top-k_classification_loss}, and task 3 general
single       sentence       classification      respectively      in      Equ.
\ref{eq:classification_loss}.

\begin{align}
  \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K + \alpha_C \mathcal{L}^C
  \label{eq:joint_SFC_loss}
\end{align}

>>>>

\section{Methodology}
In  this section, we describe our proposed SFC method, which includes the basic 2-stage SFC and its more compact version joint-SFC.

\subsection{2-stage SFC}

@@

\vspace{-2em}
\begin{equation}
  \begin{aligned}
    \mathcal{L}^{C}&=\frac{1}{N}\sum_{i=1}^{N}-log(\frac{exp(\varPhi_{i,y_{i}}^C)}{\sum_{j=1}^{C}exp(\varPhi_{i,j}^C)}) \\
    \label{eq:classification_loss}
  \end{aligned}
\end{equation}
\vspace{-2.5em}

@@

\begin{table*}
  \begin{centering}
    \scalebox{0.75}{
      \begin{tabular}{|c|c|c|c|c|c|}
        \hline 
        \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} &
        \textbf{\#Training Samples} & \textbf{\#Samples/Class} & \textbf{Settings}\tabularnewline
        \hline 
        ITG & FAQ chatbot & 228 & 3938 * 0.7 & 12 & 3-fold\tabularnewline
        \hline 
        Amazon-670k & Product review & 250 & 2658 * 0.7 & 8 & 3-fold\tabularnewline
        \hline 
        HWU64 & Intent detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
        CLINC150 & Intent detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
        BANKING77 & Intent detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
        FRAMES & Intent detection with NER & 21 & [208, 408, 984] & [10, 20, 50] & data sampling\tabularnewline
        \hline
        ATIS & Intent detection with NER & 21 & [168, 303, 544] & [10, 20, 50] & data sampling\tabularnewline
        \hline
      \end{tabular}
    }
    \par
  \end{centering}
  \caption{Statistics for all datasets and few shot settings.}

@@

\vspace{-1.5em}
\begin{equation}
  \begin{aligned}
    \mathcal{L}^{S}&=\frac{1}{M}\sum_{i=1}^{M}-w^S_{l_i}\cdot log(\frac{exp(\varPhi_{i,l_{i}}^S)}{\sum_{j=0}^{1}exp(\varPhi_{i,j}^S)}) \\
    \label{eq:similarity_loss}
  \end{aligned}
\end{equation}
\vspace{-2em}

@@

\vspace{-2em}
\begin{align}
  {\xi}_{i,j}^{K,pos} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,pos} \ \ \ \ \ \ \ 
  {\xi}_{i,j}^{K,neg} = \sum_{p=1}^{P}{\varPhi}_{i,j,p}^{K,neg}
  \label{eq:average pooling}
\end{align}

@@

\begin{align}
  \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K
  \label{eq:two-stage_SFC_loss}
\end{align}
\vspace{-2em}

@@

    \scalebox{0.475}{

@@

        \multirow{2}*{Joint-SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.9669}$} & \multirow{2}*{$\textbf{0.9712}$} & \multirow{2}*{$\textbf{0.9821}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.9323}$} & \multirow{2}*{$\textbf{0.9463}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$\textbf{0.7593}$} & \multirow{2}*{$\textbf{0.7772}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline

@@

\subsection{Joint-SFC}
In  2-stage  SFC,  Stage  1  and  stage 2 are separate that there is no deep
interaction  with each other during training. In this case, the performance of
stage  1  may  limit  the potential of stage 2; meanwhile, stage 2 also cannot
give  training feedback back to stage 1 for fine-tuning. Therefore, to further
improve  the  overall performance of SFC, we proposed a joint model structure,
shown in Fig. \ref{fig:framework}.

In  joint-SFC,  classification  model is being placed in lower layer level to
dynamically  provide  top-K  candidate  class  labels  for  the  sentence-pair
similarity  model  placed in higher layer level through a top-K pooling layer.
In  this way, classification model and similarity model can be merged into one
single  joint-model  for  multi-task training with sentence pairs sampled from
varying  candidate  class  labels,  thus  avoiding the limitation brought by 2
separate stage structure.

There  are 3 tasks in total during the training process of joint-SFC, shown in
Fig. \ref{fig:framework}, and the overall loss is also the weighted sum of all
the   task-specific  losses,  shown  in  Equ.  \ref{eq:joint_SFC_loss}.  Here,
$\alpha_S$,  $\alpha_K$  and  $\alpha_C$  represent  the  weights  for  task 1
sentence-pair  similarity  in  Equ.  \ref{eq:similarity_loss},  task  2  top-K
classification  in Equ. \ref{eq:top-k_classification_loss}, and task 3 general
single       sentence       classification      respectively      in      Equ.
\ref{eq:classification_loss}.

\vspace{-1.5em}
\begin{align}
  \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K + \alpha_C \mathcal{L}^C
  \label{eq:joint_SFC_loss}
\end{align}
\vspace{-1.5em}
